---
title: "Tranexamic acid PBPK modeling"
author: "Yuezhe Li"
date: "Jun 20, 2022"
output: html_document
---

# Set up
```{r setup, include=FALSE, echo = FALSE}
rm(list=ls())
gc()

library(tidyverse)
library(mrgsolve)
library(ggplot2)
library(gridExtra)
library(PKPDmisc)

## adjust general theme for plotting
th <- theme(plot.title=element_text(size=20), axis.title=element_text(size=10),
            axis.text=element_text(size=10), legend.text=element_text(size=20))
```

# Calculate partition coefficient of tranexamic acid

## Berezhkovskiy, 2004
```{r}
calcKp_Berez <- function(logP, pKa, fup, BP=1, type=1, dat){

  dat_all <- dat %>% filter(!tissue %in% c("Plasma","Adipose","RBCs"))
  
  n <- length(dat$tissue)
  Kp_all <- vector(mode = "numeric", length = n)
  
  Vwp <- dat$f_water[dat$tissue == "Plasma"]
  Vnlp <- dat$f_n_l[dat$tissue == "Plasma"]
  Vphp <- dat$f_pl[dat$tissue == "Plasma"]
  
  dat2 <- dat %>% filter(!tissue %in% c("Plasma","RBCs"))
  
  Vwt <- dat2$f_water[dat2$tissue != "Adipose"]
  Vwad <- dat2$f_water[dat2$tissue == "Adipose"]
  Vnlt <- dat2$f_n_l[dat2$tissue != "Adipose"]
  Vnlad <- dat2$f_n_l[dat2$tissue == "Adipose"]
  Vpht <- dat2$f_pl[dat2$tissue != "Adipose"]
  Vphad <- dat2$f_pl[dat2$tissue == "Adipose"]
  
  fut <- 1/(1+((1-fup)/fup)*0.5)
  
  pH <- dat$pH[dat$tissue == "Adipose"]

  logD <- 1.115*logP-1.35 #logD is the olive oil:buffer(water) partition coefficient of nonionized species
  
  logD_star <- switch(type,
                      #1-neutral
                      logD,   
                      #2-monoprotic acid
                      logD-log10(1+10^(pH-pKa)),
                      #3-monoprotic base
                      logD-log10(1+10^(pKa-pH)), 
                      #4-diprotic acid
                      logD-log10(1+10^(2*pH-pKa[1]-pKa[2])),
                      #5-diprotic base
                      logD-log10(1+10^(pKa[1]+pKa[2]-2*pH)), 
                      #6-monoprotic acid monoprotic base (acid comes first)
                      logD-log10(1+10^(pKa[2]-pKa[1])),  
                      #7-triprotic acid
                      logD-log10(1+10^(3*pH-pKa[1]-pKa[2]-pKa[3])),  
                      #8-triprotic base
                      logD-log10(1+10^(pKa[1]+pKa[2]+pKa[3]-3*pH)),  
                      #9-diprotic acid monoprotic base (first two are acid)
                      logD-log10(1+10^(pH-pKa[1]-pKa[2]+pKa[3])), 
                      #10-diprotic base monoprotic acid (first one is acid)
                      logD-log10(1+10^(pKa[2]+pKa[3]-pKa[1]-pH)))       
  
  D_star <- 10^logD_star   
  Kpad <- ((D_star*(Vnlad+0.3*Vphad)+((Vwad/fut)+0.7*Vphad))/(D_star*(Vnlp+0.3*Vphp)+((Vwp/fup)+0.7*Vphp)))

  
  P <- 10^logP
  Kpt <- ((P*(Vnlt+0.3*Vpht)+((Vwt/fut)+0.7*Vpht))/(P*(Vnlp+0.3*Vphp)+((Vwp/fup)+0.7*Vphp))) 
  
  nms_all <- dat_all$tissue %>% substr(1,2) %>% tolower()
  nms_all <- paste("Kp", nms_all, sep="")
  nms <- c("Kpad",nms_all)
  # return(nms)
  Kp <- as.list(c(Kpad,Kpt))
  names(Kp) <- nms
  
  return(Kp)
}
```

## Poulin and Theil http://jpharmsci.org/article/S0022-3549(16)30889-9/fulltext
```{r}
calcKp_PT <- function(logP= -1.43, pKa = 11.8, fup = 1, BP=1, type=3, dat){
  
  dat_all <- dat %>% filter(!tissue %in% c("Plasma","Adipose","RBCs"))
  
  n <- length(dat$tissue)
  Kp_all <- vector(mode = "numeric", length = n)
  
  Vwp <- dat$f_water[dat$tissue == "Plasma"]
  Vnlp <- dat$f_n_l[dat$tissue == "Plasma"]
  Vphp <- dat$f_pl[dat$tissue == "Plasma"]
  
  dat2 <- dat %>% filter(!tissue %in% c("Plasma","RBCs"))
  
  Vwt <- dat2$f_water[dat2$tissue != "Adipose"]
  Vwad <- dat2$f_water[dat2$tissue == "Adipose"]
  Vnlt <- dat2$f_n_l[dat2$tissue != "Adipose"]
  Vnlad <- dat2$f_n_l[dat2$tissue == "Adipose"]
  Vpht <- dat2$f_pl[dat2$tissue != "Adipose"]
  Vphad <- dat2$f_pl[dat2$tissue == "Adipose"]
    
  pH <- dat$pH[dat$tissue == "Adipose"]
  logD <- 1.115*logP-1.35 #logD is the olive oil:buffer(water) partition coefficient of nonionized species
  
  logD_star <- switch(type,
                 #1-neutral
                 logD,   
                 #2-monoprotic acid
                 logD-log10(1+10^(pH-pKa)),
                 #3-monoprotic base
                 logD-log10(1+10^(pKa-pH)), 
                 #4-diprotic acid
                 logD-log10(1+10^(2*pH-pKa[1]-pKa[2])),
                 #5-diprotic base
                 logD-log10(1+10^(pKa[1]+pKa[2]-2*pH)), 
                 #6-monoprotic acid monoprotic base (acid comes first)
                 logD-log10(1+10^(pKa[2]-pKa[1])),  
                 #7-triprotic acid
                 logD-log10(1+10^(3*pH-pKa[1]-pKa[2]-pKa[3])),  
                 #8-triprotic base
                 logD-log10(1+10^(pKa[1]+pKa[2]+pKa[3]-3*pH)),  
                 #9-diprotic acid monoprotic base (first two are acid)
                 logD-log10(1+10^(pH-pKa[1]-pKa[2]+pKa[3])), 
                 #10-diprotic base monoprotic acid (first one is acid)
                 logD-log10(1+10^(pKa[2]+pKa[3]-pKa[1]-pH)))       

  D_star <- 10^logD_star   
  Kpad <- ((D_star*(Vnlad+0.3*Vphad)+(1*(Vwad+0.7*Vphad)))/(D_star*(Vnlp+0.3*Vphp)+(1*(Vwp+0.7*Vphp)))) * fup
      
  P <- 10^logP
  fut <- 1/(1+((1-fup)/fup)*0.5)
  Kpt <- ((P*(Vnlt+0.3*Vpht)+(1*(Vwt+0.7*Vpht)))/(P*(Vnlp+0.3*Vphp)+(1*(Vwp+0.7*Vphp)))) * (fup/fut)
  
  nms_all <- dat_all$tissue %>% substr(1,2) %>% tolower()
  nms_all <- paste("Kp", nms_all, sep="")
  nms <- c("Kpad",nms_all)
  Kp <- as.list(c(Kpad,Kpt))
  names(Kp) <- nms
  
  return(Kp)
}
```

## Calculation
```{r}
dat <- read.csv("tissue_comp_P_T.csv")
logP <- -1.79  #liphilicity; https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8299544/
pKa <- 10.28 
fup <- 1  # unbound fraction in plasma
type <- 1  # monoprotic base
BP <- 3  #blood:plasma concentration ratio

kp_pt <- calcKp_PT(logP=logP, pKa=pKa, fup=fup, BP=BP, type=type, dat=dat) # the original 
kp_berez <- calcKp_Berez(logP, pKa=pKa, fup=fup, BP=BP, type=type, dat=dat)
```


# Observed data

Data observed from Pilbrant et al., 1981
https://pubmed.ncbi.nlm.nih.gov/7308275/
```{r}
time_iv <- c(1/6, 2/6, 0.5, 1, 1.5, 2, 3, 4, 7, 9.5, 12, 24, 30, 32)

# plasma concentration after IV dose of 1g tranexamic acid
# unit: mg/L
ll <- data.frame(time = time_iv, obs = c(86, 61, 49, 31, 25.1, 20.5, 14.4, 9, 5.1, 2.3, 0.91, 0.27, 0.22, 0.22)) # wt = 66kg
oe <- data.frame(time = time_iv, obs = c(86, 65.6, 47.1, 32.3, 25.9, 17.4, 12, 7.6, 3.3, 2.2, 1.3, 0.45, 0.26, 0.25)) # wt = 80kg
sn <- data.frame(time = time_iv, obs = c(81.8, 63.8, 44.4, 31.7, 25, 20.8, 13, 9.3, 4, 2.1, 1.3, 0.3, 0.23, 0.22)) # wt = 73kg

# plasma concentration afteroral dose of 2g tranexamic acid
# unit: mg/L
time_oral <- c(0.5, 1, 1.5, 2,3,4,5,6)
oral1 <- data.frame(time = time_oral, obs = c(0.4, 11.4, 14.1, 16.4, 15.4, 12.6, 8.5, 6.1))
oral2 <- data.frame(time = time_oral, obs = c(3.4, 10.3, 14.7, 17.7, 16.4, 12.8, 8, 3.2))
oral3 <- data.frame(time = time_oral, obs = c(2.1, 9.1, 9.7, 9.3, 9.1, 6.9, 5.5, 4.2))
oral4 <- data.frame(time = time_oral, obs = c(6.4, 13.3, 15.8, 15.6, 17.9, 14.5, 10.9, 7.4))
oral5 <- data.frame(time = time_oral, obs = c(0.5, 4.6, 9.1, 10.5, 12.4, 12, 9.5, 6.3))
oral6 <- data.frame(time = time_oral, obs = c(3, 8.6, 10.5, 11.8, 15.7, 12.4, 10.9, 7.7))
oral7 <- data.frame(time = time_oral, obs = c(3.9, 7.1, 8.6, 9.3, 10.1, 8.2, 6.7, 4.4))
oral8 <- data.frame(time = time_oral, obs = c(1.3, 5.5, 8.8, 12.3, 13.1, 15.2, 12.3, 7.7))
oral9 <- data.frame(time = time_oral, obs = c(2.3, 7.7, 12.6, 15.4, 16.3, 14.9, 9.6, 7.4))
oral10 <- data.frame(time = time_oral, obs = c(2.2, 6.1, 10.2, 12.2, 12.4, 10.7, 10.4, 9.3))
```

# Read model

```{r}
modA <- mread("TranexamicAcidPBPK") %>% param(hepatic_scaling = 0) # based on Dunn et al., 1999
# https://pubmed.ncbi.nlm.nih.gov/10400410/
```

# Model validation

IV dose = 1g
```{r}
MW = 157.21 # unit: g.mol-1

dose = 1 # unit = g

sim1 <- modA %>% 
  param(BP = 3) %>%
  param(kp_pt) %>%
  ev(time=0, amt=dose/MW, cmt='VEN') %>% 
  mrgsim(delta = 0.05, end = 32) %>% as_tibble() %>% filter(time > 0.01)

iv1g <- ggplot() + 
  geom_line(data = sim1, aes(x = time, y = Cvenous * MW * 1000, col = "plasma, predicted"), alpha = 0.9) +  
  # geom_line(data = sim1, aes(x = time, y = Cskin * MW * 1000, col = "skin"), alpha = 0.9) +  
  geom_line(data = sn, aes(x = time, y = obs, col = "plasma, subj S.N."), alpha = 0.5, linetype="dashed") +
  geom_point(data = sn, aes(x = time, y = obs, col = "plasma, subj S.N."), alpha = 0.5, size = 3) +
  geom_line(data = oe, aes(x = time, y = obs, col = "plasma, subj O.E."), alpha = 0.5, linetype="dashed") +
  geom_point(data = oe, aes(x = time, y = obs, col = "plasma, subj O.E."), alpha = 0.5, size = 3) +
  geom_line(data = ll, aes(x = time, y = obs, col = "plasma, subj L.L."), alpha = 0.5, linetype="dashed") +
  geom_point(data = ll, aes(x = time, y = obs, col = "plasma, subj L.L."), alpha = 0.5, size = 3) +
  # scale_y_continuous(trans = "log10", limits = c(1e-4, 100)) + 
  labs(x = "time (h)", y = "concentration (mg/L)", color = "") + theme_bw() + ggtitle("IV, dose = 1g")

iv1g
```
Oral dose = 2g

```{r}
MW = 157.21 # unit: g.mol-1
bioavailability = 0.3 # https://pubmed.ncbi.nlm.nih.gov/10400410/

dose = 2

sim2 <- modA %>% 
  param(BP = 3) %>%
  param(kp_pt) %>%
  param(ka = 0.4) %>% # tuned
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 6) %>% as_tibble() %>% filter(time > 0.1)

oral2g <- ggplot() + 
  geom_line(data = sim2, aes(x = time, y = Cvenous * MW * 1000, col = "plasma, predicted"), alpha = 0.9) +  
  geom_line(data = oral1, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral1, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  geom_line(data = oral2, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral2, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  geom_line(data = oral3, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral3, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  geom_line(data = oral4, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral4, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  geom_line(data = oral5, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral5, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  geom_line(data = oral6, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral6, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  geom_line(data = oral7, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral7, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  geom_line(data = oral8, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral8, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  geom_line(data = oral9, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral9, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  geom_line(data = oral10, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, linetype="dashed") +
  geom_point(data = oral10, aes(x = time, y = obs, col = "plasma obs"), alpha = 0.5, size = 3) +
  labs(x = "time (h)", y = "concentration (mg/L)", color = "") + theme_bw() + ggtitle("oral, dose = 2g")
  
oral2g
```
Save validation figures

```{r}
png('img/validation.png', width = 1200, height = 400, res = 100)
grid.arrange(iv1g, oral2g, ncol = 2)
dev.off()
```

# Skin-focused study

```{r}
modB <- modA %>% param(BP = 3) %>% param(kp_pt) %>% 
                 param(ka = 0.4) # tuned
```

## single dose skin dynamics

```{r}
# oral dose = 1.5g
dose = 1.5

sim3 <- modB %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 12) %>% as_tibble() %>% filter(time > 0.1)

skinconc1 = ggplot() + 
  geom_line(data = sim3, aes(x = time, y = Cskin * MW * 1000, col = "skin, predicted"), alpha = 0.9) +
  geom_hline(yintercept = 3.79, show.legend = NA, color  = 'blue') + 
  labs(x = "time (h)", y = "concentration (mg/L)", color = "") + theme_bw() 


skinconc2 = ggplot() + 
  geom_line(data = sim3, aes(x = time, y = Cskin * 1e6, col = "skin, predicted"), alpha = 0.9) +
  geom_hline(yintercept = 1.1, show.legend = NA, color  = 'blue') + 
  labs(x = "time (h)", y = "skin concentration (uM)", color = "") + theme_bw() + 
  theme(legend.position="bottom") 


plasmaconc1 = ggplot() + 
  geom_line(data = sim3, aes(x = time, y = Cvenous * MW * 1000, col = "plasma, predicted"), alpha = 0.9) +
  geom_hline(yintercept = 10, show.legend = NA, color  = 'blue') + 
  labs(x = "time (h)", y = "plasma concentration (mg/L)", color = "") + theme_bw()  + 
  theme(legend.position="bottom") 


png('img/SingleDoseSkinPlasma.png', width = 1200, height = 400, res = 100)
grid.arrange(skinconc2, plasmaconc1, ncol = 2)
dev.off()

grid.arrange(skinconc2, plasmaconc1, ncol = 2)
```


## multiple oral dose 

Effective TXA concentration obtained from Picetti et al., 2019
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6365258/
```{r}
# oral dose = 1.5g
dose = 1.5

sim4 <- modB %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN', addl = 4, ii = 12) %>% 
  mrgsim(delta = 0.1, end = 24*3) %>% as_tibble() %>% filter(time > 0.1)

OralMulti <- ggplot() + 
  geom_line(data = sim4, aes(x = time, y = Cvenous * MW * 1000, col = "plasma, predicted"), alpha = 0.9) +  
  geom_line(data = sim4, aes(x = time, y = Cskin * MW * 1000, col = "skin, predicted"), alpha = 0.9) +
  geom_hline(yintercept = 10, show.legend = NA, color = 'green', linetype="dashed") + 
  geom_hline(yintercept = 1.1e-6 * MW, show.legend = NA, color = 'blue', linetype="dashed") + 
  scale_x_continuous(breaks = c(0, 12, 24, 36, 48, 60, 72)) + 
  # scale_y_continuous(trans = "log") + 
  labs(x = "time (h)", y = "concentration (mg/L)", color = "") + theme_bw()

OralMulti

ggsave(file = 'img/MultiDoseSkinPlasma.png', plot = OralMulti, width = 8, height = 4)
```

## Compare exposure 

```{r}
auc = auc_partial(sim4$time, sim4$Cadipose)[[1]] %>% data.frame()
names(auc) = "AUC"
auc['organ'] = 'Adipose'

auc[2,1] = auc_partial(sim4$time, sim4$Cbrain)[[1]]
auc[2,2] = 'Brain'

auc[3,1] = auc_partial(sim4$time, sim4$Cheart)[[1]]
auc[3,2] = 'Heart'

auc[4,1] = auc_partial(sim4$time, sim4$Cbone)[[1]]
auc[4,2] = 'Bone'

auc[5,1] = auc_partial(sim4$time, sim4$Ckidney)[[1]]
auc[5,2] = 'Kidney'

auc[6,1] = auc_partial(sim4$time, sim4$Cliver)[[1]]
auc[6,2] = 'Liver'

auc[7,1] = auc_partial(sim4$time, sim4$Clung)[[1]]
auc[7,2] = 'Lung'

auc[8,1] = auc_partial(sim4$time, sim4$Cmuscle)[[1]]
auc[8,2] = 'Muscle'

auc[9,1] = auc_partial(sim4$time, sim4$Cspleen)[[1]]
auc[9,2] = 'Spleen'

auc[10,1] = auc_partial(sim4$time, sim4$Crest)[[1]]
auc[10,2] = 'Rest'

auc[11,1] = auc_partial(sim4$time, sim4$Cvenous)[[1]]
auc[11,2] = 'Plasma'

auc[12,1] = auc_partial(sim4$time, sim4$Cskin)[[1]]
auc[12,2] = 'Skin'


exposure <- ggplot(auc, aes(x = reorder(organ, -AUC), y = AUC)) +
  geom_col(fill = "whitesmoke", color = 'gray8') +
  labs(x = "", y = "exposure (mol/L.h)") + theme_bw() + ggtitle('exposure after 7.5g TXA over 72 hours')

exposure

ggsave(file = 'img/Exposure.png', plot = exposure, width = 8, height = 4)
```

# Sensitivity Analysis

## blood:plasma ratio

```{r}
kp_pt_1 <- calcKp_PT(logP=logP, pKa=pKa, fup=fup, BP=1, type=type, dat=dat) # BP = 1 
kp_pt_3 <- calcKp_PT(logP=logP, pKa=pKa, fup=fup, BP=3, type=type, dat=dat) # BP = 3 
kp_pt_5 <- calcKp_PT(logP=logP, pKa=pKa, fup=fup, BP=5, type=type, dat=dat) # BP = 5 
kp_pt_9 <- calcKp_PT(logP=logP, pKa=pKa, fup=fup, BP=9, type=type, dat=dat) # BP = 9 

mod1 <- modB %>% param(ka = 0.4) %>% param(BP = 1) %>% param(kp_pt_1) 
mod3 <- modB %>% param(ka = 0.4) %>% param(BP = 3) %>% param(kp_pt_3) 
mod5 <- modB %>% param(ka = 0.4) %>% param(BP = 5) %>% param(kp_pt_5) 
mod9 <- modB %>% param(ka = 0.4) %>% param(BP = 9) %>% param(kp_pt_9) 


sim01 <- mod1 %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 12) %>% as_tibble() %>% filter(time > 0.1)

sim03 <- mod3 %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 12) %>% as_tibble() %>% filter(time > 0.1)

sim05 <- mod5 %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 12) %>% as_tibble() %>% filter(time > 0.1)

sim09 <- mod9 %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 12) %>% as_tibble() %>% filter(time > 0.1)

bpscan <- ggplot() + 
  geom_line(data = sim01, aes(x = time, y = Cskin, color = "BP=1")) + 
  geom_line(data = sim03, aes(x = time, y = Cskin, color = "BP=3")) + 
  geom_line(data = sim05, aes(x = time, y = Cskin, color = "BP=5")) + 
  geom_line(data = sim09, aes(x = time, y = Cskin, color = "BP=9")) + 
  labs(x = "time (h)", y = "skin concentration (mol/L)", color = "") + theme_bw()

bpscan

ggsave(file = 'img/sens_BP.png', plot = bpscan, width = 8, height = 4)
```
## Oral TXA absorption rate

```{r}
sim10 <- modB %>% 
  idata_set(expand.idata(ka = c(0.04, 0.2, 0.4, 0.8, 4))) %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 12) %>% as_tibble() %>% filter(time > 0.1)

kascan <- ggplot(data = sim10, aes(x = time, y = Cskin)) + 
  geom_line(data = sim10 %>% filter(ID==1), aes(col = "ka = 0.04h-1")) + 
  geom_line(data = sim10 %>% filter(ID==2), aes(col = "ka = 0.2h-1")) + 
  geom_line(data = sim10 %>% filter(ID==3), aes(col = "ka = 0.4h-1")) + 
  geom_line(data = sim10 %>% filter(ID==4), aes(col = "ka = 0.8h-1")) + 
  geom_line(data = sim10 %>% filter(ID==5), aes(col = "ka = 4h-1")) + 
  labs(x = "time (h)", y = "skin concentration (mol/L)", color = "") + theme_bw()
  
kascan

ggsave(file = 'img/sens_ka.png', plot = kascan, width = 8, height = 4)
```

## Body weight 

```{r}
sim20 <- modB %>% param(WEIGHT = 73) %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 12) %>% as_tibble() %>% filter(time > 0.1)

sim21 <- modB %>% param(WEIGHT = 80.3) %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 12) %>% as_tibble() %>% filter(time > 0.1)

weightscan <- ggplot(data = sim20, aes(x = time, y = Cskin)) + 
  geom_line(data = sim20, aes(col = "weight = 73kg")) + 
  geom_line(data = sim21, aes(col = "weight = 80.3kg")) + 
  labs(x = "time (h)", y = "skin concentration (mol/L)", color = "") + theme_bw()

weightscan

ggsave(file = 'img/sens_weight.png', plot = weightscan, width = 8, height = 4)
```

## Renal impairment

```{r}
sim30 <- modB %>% 
  # renal impairment based on FDA guidance
  idata_set(expand.idata(renal_scaling = c(14/90, 29/90, 59/90, 89/90, 1))) %>% 
  ev(time=0, amt=dose/MW * bioavailability, cmt='GUTLUMEN') %>% 
  mrgsim(delta = 0.1, end = 12) %>% as_tibble() %>% filter(time > 0.1)

renalscan_skin <- ggplot(data = sim30, aes(x = time, y = Cskin)) + 
  geom_line(data = sim30 %>% filter(ID==1), aes(col = "end stage")) + 
  geom_line(data = sim30 %>% filter(ID==2), aes(col = "severe")) + 
  geom_line(data = sim30 %>% filter(ID==3), aes(col = "moderate")) + 
  geom_line(data = sim30 %>% filter(ID==4), aes(col = "mild")) + 
  geom_line(data = sim30 %>% filter(ID==5), aes(col = "normal")) + 
  labs(x = "time (h)", y = "TXA concentration (mol/L)", color = "") + theme_bw() + ggtitle("skin")

renalscan_plasma <- ggplot(data = sim30, aes(x = time, y = Cvenous)) + 
  geom_line(data = sim30 %>% filter(ID==1), aes(col = "end stage")) + 
  geom_line(data = sim30 %>% filter(ID==2), aes(col = "severe")) + 
  geom_line(data = sim30 %>% filter(ID==3), aes(col = "moderate")) + 
  geom_line(data = sim30 %>% filter(ID==4), aes(col = "mild")) + 
  geom_line(data = sim30 %>% filter(ID==5), aes(col = "normal")) + 
  labs(x = "time (h)", y = "TXA concentration (mol/L)", color = "") + theme_bw() + ggtitle("plasma")

grid.arrange(renalscan_skin, renalscan_plasma, ncol = 1)

png('img/sens_renal.png', width = 1000, height = 400, res = 100)
grid.arrange(renalscan_skin, renalscan_plasma, ncol = 1)
dev.off()
```